CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-06 paper_I/ms.tex
update paper

@@

\begin{figure}[!t]
	\gridline{\fig{tls_sde_vs_period_scatter.pdf}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    Transiting planet search periodogram summary.
    Each point represents the TLS periodogram peak signal detection
    efficiency (SDE) and corresponding period from one light curve.
    Significance thresholds (orange lines) are empirically defined for
    the transiting planet search described in
    \S~\ref{subsec:identifying_variability}.  
    {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
	}
	\label{fig:tlsresults}
\end{figure}

Below, we provide a few examples of how one might go about identifying
pulsating stars, strong stellar rotators, eclipsing binaries, and
transiting planets in the light curves.

@@

%FIXME
%FIXME
%FIXME
%FIXME

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{quilt_s6_s7.pdf}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Phased light curves for a few objects of interest.
		{\it Top row, left to right}:
		TOI~496, in NGC 2548;
		TOI~625;
		an eccentric EB, masquerading as a planet.
		{\it Middle row, left to right}:
		A detached EB in a 80~Myr old cluster;
		V684 Mon (a 10 Myr old detached EB);
		a semi-detached EB in NGC 2548.
		{\it Bottom row, left to right}:
		Spotted rotator in NGC 2184;
		Pulsator or perhaps EB, flagged by \citet{zari_3d_2018} as a pre-MS star;
		Quasi-periodic pulsator, also with a pre-MS host.
		Gaia source identifiers are given in a footnote.
	\label{fig:quilt}
	}
\end{figure*}

@@

A detailed search for transiting planets will be the subject of future
work.
The light curves provide opportunities for studying many other types of
variables, including
pulsating stars, rotators, and eclipsing binaries.
A few hand-picked examples are shown in Figure~\ref{fig:quilt}.
The soure identifiers are in a footnote\footnote{
	Top-left to bottom-right:
	3064530810048196352, 
	3080104185367102592, 
	3027361888196408832,
	3125738423345810048,
	3326715714242517248,
	3064487241899832832,
	3024952755135530496,
	2949587413510194688, 
	5274902193830445312 
}.

@@
